---
title: "HW-ML"
author: "Thunkarn V."
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

# **Introduction**
This report is part of DataRockie Bootcamp 8 in the Machine Learning Sprint. We studied and analyzed the house price dataset in India, and trying to find the best price prediction model from linear regression.

## Library install and import data
```{r message=FALSE}
library(tidyverse)
library(caret)
library(readxl)

my_data <- read_excel("House Price India.xlsx")
```

## Data cleaning
### check missing values check
```{r message=TRUE}
my_data %>%
  complete.cases() %>%
  mean()
```
### drop row with missing values
```{r}
clean_data <- my_data %>%
  drop_na()
```
### remove unnecessary data
Since it doesn't make sense to consider id, Date, Latitude, Longitude, and postal code to predict house price, we remove them.
```{r}
use_data <- clean_data %>%
  select(-`id`, -Date, -Lattitude, -Longitude, -`Postal Code`)
```

## 1. Run a regression with all variables, then select the top 5 most important variables to run in model 2.
### 1-1 Split data
```{r}
tt_split1 <- function(data){
  set.seed(42)
  n <- nrow(data)
  id1 <- sample(n, size=0.8*n)
  train_data1 <- data [id1, ]
  test_data1 <- data [-id1, ]
  return(list(training=train_data1,
         testing=test_data1))
}

prep_data1 <- tt_split1(use_data)
train_df1 <- prep_data1[[1]]
test_df1 <- prep_data1[[2]]
```
### 1-2 train model
```{r}
lm_model1 <- train(Price~.,
                  data = train_df1,
                  method = "lm")
```
### 1-3 score
```{r}
p1 <- predict(lm_model1, newdata = test_df1)
```
### 1-4 evaluate
```{r}
mae1 <- mean(abs(p1-use_data$Price))
rmse1 <- sqrt(mean((p1-use_data$Price)**2))

```
### Find key variable
```{r message=TRUE}
varImp(lm_model1)
```

The varImp() result shows that 'water present', 'living area', 'number of bedrooms', 'built year', and 'number of views' are the top five most important variables that affect the house price.

### select use data and add log price
```{r}
use_data_2 <- use_data %>%
  select(Price,
         "A" = `waterfront present`,
         "B" = `living area`,
         "C" = `number of bedrooms`,
         "D" = `Built Year`,
         "E" = `number of views`) %>%
  mutate(logp = log(Price))
```

## 2. run regression to predict the house price in India (Price)
### 2-1 split model
```{r}
tt_split2 <- function(data) {
  set.seed(43)
  n <- nrow(data)
  id2 <- sample(n, size=0.8*n)
  train_data2 <- data [id2, ]
  test_data2 <- data [-id2, ] 
}

prep_data2 <- tt_split1(use_data_2)
train_df2 <- prep_data2[[1]]
test_df2 <- prep_data2[[2]]
```
### 2-2 train model
```{r}
lm_model2 <- train(Price~.,
                  data = train_df2,
                  method = "lm")
```
### 2-3 score
```{r}
p2 <- predict(lm_model2, newdata = test_df2)
```
### 2-4 evaluate
```{r}
mae2 <- mean(abs(p2-use_data_2$Price))
rmse2 <- sqrt(mean((p2-use_data_2$Price)**2))
```

## 3. run regression to predict the house price in India (log(Price))
### 3-1 split data can use from model 2

### 3-2 Train model
```{r}
lm_model3 <- train(logp~.,
                   data = train_df2,
                   method = "lm")

p_train_3 <- predict(lm_model3, newdata = train_df2)

mae_train_model_3 <- mean(abs(exp(p_train_3)-exp(use_data_2$logp)))
rmse_train_model_3 <- sqrt((mean(exp(p_train_3)-exp(use_data_2$logp))**2))
```

### 3-3 score
```{r}
p3 <- predict(lm_model3, newdata = test_df2)
```

### 3-4 evaluate
```{r}
mae3 <- mean(abs(exp(p3)-exp(use_data_2$logp)))
rmse3 <- sqrt((mean(exp(p3)-exp(use_data_2$logp))**2))
```

## Summarize RMSE train vs test
### Model 1 
```{r}
print(lm_model1$results$RMSE)
print(rmse1)
```

### Model 2 
```{r}
print(lm_model2$results$RMSE)
print(rmse2)
```
### Model 3 
```{r}
print(rmse_train_model_3)
print(rmse3)
```

## Summarize MAE train vs test
### Model 1 
```{r}
print(lm_model1$results$MAE)
print(mae1)
```

### Model 2 
```{r}
print(lm_model2$results$MAE)
print(mae2)
```
### Model 3 
```{r}
print(mae_train_model_3)
print(mae3)
```
