---
title: "Data Visualization Bootcamp homework"
author: "Thunkarn V."
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Introduction
This report is part of DataRockie Bootcamp 8 in the data visualization sprint. We studied and analyzed the Diamonds dataset to learn more about the relationships between the parameters.

## Data overview
quick overview of a data frame

```{r}
library(tidyverse)
glimpse(diamonds)
```

### Question 1

```{r}
## relation between clarity and cut
library(ggplot2)
ggplot(diamonds, aes(x=clarity, fill = cut)) +
  geom_bar(position = "fill") +
  theme_minimal() +
  scale_fill_manual(values = 
                      c("#afcede", "#7eb9d6", "#7eb9d6", 
                        "#7eb9d6", "#0467c9")) +
  labs(
    title = "relation between clarity and cut",
    caption = "Source : Dataset diamonds, R studio"
  )
```

From this bar chart we found that the higher clarity, the better cut quality of the diamonds

### Question 2
Color VS price

```{r}
## relation between color and price
ggplot(diamonds, aes(x=color, y=price)) +
  geom_violin() +
  theme_minimal() +
    labs(
    title = "relation between color and price",
    caption = "Source : Dataset diamonds, R studio"
    )
```
```{r}
diamonds %>%
  group_by(color) %>%
  summarise(
    median(price),
    mean(price),
    min(price),
    max(price)
  )
```

The violin plot above shows that color quality is significantly related to price. However, the minimum and maximum data suggest that there may be another factor involved.

Question 3
Carat VS Price

```{r}
set.seed(43)
 sample_diamonds <- sample_frac(diamonds, 0.25)

ggplot(sample_diamonds, aes(x=carat, y=price)) +
  geom_point() +
  theme_minimal()
```

```{r}
sample_diamonds %>%
  select(carat,price) %>%
  cor()
```

The scatter plot above shows that carat has a significant effect on the price of diamonds. This is also confirmed by the correlation between carat and price, which is very close to one.


### Question 4 
Clarity VS Price(without considering carat)

```{r}
set.seed(43)
 sample_diamonds <- sample_frac(diamonds, 0.25)
 
sample_diamonds2 <- sample_diamonds %>%
  mutate(price_per_carat = price/carat)

```

```{r}
ggplot(sample_diamonds2, aes(x=clarity, y=price_per_carat))+
  geom_boxplot() +
  theme_minimal() +
      labs(
    title = "relation between clarity and price per Carat",
    caption = "Source : Dataset diamonds, R studio",
    x = "Diamonds clarity",
    y = "Price per Carat"
    )
```

```{r}
sample_diamonds2 %>%
  group_by(clarity) %>%
  summarise(
    median = round(median(price_per_carat)),
    average = round(mean(price_per_carat)),
    min = round(min(price_per_carat)),
    max= round(max(price_per_carat))
  )
```

The box plot above shows that without considering the Carat factor, clarity has no relation with price. This conclusion is also confirmed by the summary table.

### Question 5
Depth VS Price(without considering carat) split by cut type
```{r}
ggplot(sample_diamonds2, aes(x=depth, y=price_per_carat)) +
  geom_point() +
  geom_smooth(method = "lm", col="red") +
  facet_wrap(~cut, ncol=2) +
  theme_minimal() +
    labs(title = "Relationship between depth and price per carat by cut",
       x = "depth",
       y = "price per carat",
       caption = "Source: Diamonds from ggplot2 package")
```
```{r}
sample_diamonds2 %>%
  select(price_per_carat, depth) %>%
  cor()
```

The scatter plot above shows that depth has very little relation with price per carat. This is also confirmed by the correlation coefficient, which is lower than 0.5.



